---
output:
  html_document:
    toc: yes
    df_print: paged
  html_notebook:
    toc: yes
    toc_float: yes
editor_options:
  chunk_output_type: inline
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(magrittr)
library(devtools)
```

# `tsbox` - package review

## **Reviewer:** [\@chamberlinc](https://github.com/chamberlinc)

### Review Submitted:
**`r cat(sprintf("**Last updated:** %s", Sys.Date()))`**

***

<br>

This report contains documents associated with the review of **rOpenSci** submitted package:

### **`tsbox`: ropensci/software-review**  issue [\#464](https://github.com/ropensci/onboarding/issues/).

<br>

## Package info

**Description:**

Time series toolkit with identical behavior for all
  time series classes: 'ts','xts', 'data.frame', 'data.table', 'tibble', 'zoo',
  'timeSeries', 'tsibble', 'tis' or 'irts'. Also converts reliably between these classes.

**Author:** `r person("Christoph", "Sax", email = "christoph.sax@gmail.com", role = c("aut", "cre"), comment = c(ORCID = "0000-0002-7192-7044"))`

**repo url:** <https://github.com/christophsax/tsbox>

**website url:** <https://www.tsbox.help>

## Review info


#### See [reviewer guidelines](https://ropensci.github.io/dev_guide/reviewerguide.html) for further information on the rOpenSci review process.

**key review checks:**

- Does the code comply with **general principles in the [Mozilla reviewing guide](https://mozillascience.github.io/codeReview/review.html)**?
> Yes

- Does the package **comply with the [ROpenSci packaging guide](https://ropensci.github.io/dev_guide/building.html)**?
> Yes

- Are there **improvements** that could be made to the **code style?**
> Style is all ok

- Is there **code duplication** in the package that should be reduced?
- Are there **user interface improvements** that could be made?
- Are there **performance improvements** that could be made?
- Is the [**documentation**](https://ropensci.github.io/dev_guide/building.html#documentation) (installation instructions/vignettes/examples/demos) **clear and sufficient**?

Please be respectful and kind to the authors in your reviews. The rOpenSci [code of conduct](https://ropensci.github.io/dev_guide/policies.html#code-of-conduct) is mandatory for everyone involved in our review process.

***

### session info


```{r sessionInfo}
sessionInfo()
```


```{r pkg_dir, echo = F}
pkg_dir <- "C:/Users/Cathy/Documents/PeerReviewing/tsbox/tsbox"
```

## Test installation

### test local `tsbox` install:

```{r test-local}
try(install(pkg_dir, dependencies = T, build_vignettes = T))
```

```{r github-rm}
remove.packages("tsbox")
```
#### **comments:**

> Local install went without a hitch when I was not knitting the document - no errors or warnings. Errors and warnings that occur while knitting did not happen when just working through the document.

***

### test install of `tsbox` from GitHub with:

```{r test-github}
devtools::install_github("christophsax/tsbox", dependencies = T, build_vignettes = T)
```

#### **comments:**

> Github install seemed to work correctly.

***



## Check package integrity

### run checks on `tsbox` source:

```{r check-checks}
try(devtools::check(pkg_dir))
```
#### **comments:**

> First time run, this produced error `Error in loadNamespace(name) : there is no package called 'srr'`. After installing `srr` package, 1 error and 1 warning were produced. and one test was skipped. Additionally, one check gave a warning: 'qpdf' is needed for checks on size reduction of PDFs. I have qpdf installed on my machine. Below is the printout:

> library(testthat)
> library(tsbox)
> 
> test_check("tsbox")
Starting 2 test processes
== Skipped tests ===============================================================
* empty test (1)
== Warnings ====================================================================
-- Warning (test-ts_first_of_period.R:18:3): ts_first_of_period works ----------
no non-missing arguments to min; returning Inf
Backtrace:
 1. tsbox::ts_first_of_period(x)
 2. tsbox::ts_apply(x, dts_first_of_period)
 3. tsbox:::ts_apply_dts(ts_dts(x), fun, ...)
 4. tsbox:::fun(x, ...)
 8. base::NextMethod("[")
== Failed tests ================================================================
-- Error (test-ts_first_of_period.R:18:3): ts_first_of_period works ------------
Error in `max(which(time <= smry$start)):min(which(time >= smry$end))`: result would be too long a vector
Backtrace:
    x
 1. \-tsbox::ts_first_of_period(x)
 2.   \-tsbox::ts_apply(x, dts_first_of_period)
 3.     \-tsbox:::ts_apply_dts(ts_dts(x), fun, ...)
 4.       \-tsbox:::fun(x, ...)
 5.         +-time[(max(which(time <= smry$start)):min(which(time >= smry$end)))]
 6.         +-base::`[.POSIXct`(...)
 7.         | \-base::.POSIXct(NextMethod("["), attr(x, "tzone"), oldClass(x))
 8.         \-base::NextMethod("[")
[ FAIL 1 | WARN 1 | SKIP 1 | PASS 770 ]
Error: Test failures
Execution halted
1 error x | 1 warning x | 0 notes √

***

### run tests on `tsbox` source:

```{r check-tests}
devtools::test(pkg_dir)
```
#### **comments:**

> Again, there was one fail, one warning, and one skipped test. The warning was from ts_first_of_period, due to the timeseries existing of all NAs. The error was also for ts_first_of_period, that 'result would be too long a vector'. The skipped test was for tsibble back-conversion because it appears as an empty test. 

***


### check `tsbox` for goodpractice:

```{r test-goodpractice}
goodpractice::gp(pkg_dir)
```
#### **comments:**

> Returned 174 instances of lines greater than 80 characters. A quick scan of a few of these files indicates this is regularly on the lines that begin with  `@srrstats` .

***

## Check package metadata files

### inspect

- #### [README](https://github.com/christophsax/tsbox)
- #### [DESCRIPTION](https://github.com/christophsax/tsbox/blob/master/DESCRIPTION)
- #### [NAMESPACE](https://github.com/christophsax/tsbox/blob/master/NAMESPACE)

### spell check

```{r spell-check}
devtools::spell_check(pkg_dir)
```

#### **comments:**

> Metadata files look ok to me. I think the ReadMe file does a good job of demonstrating the package's capabilities without being overwhelming in detail.

***

## Check documentation

online documentation: **<https://www.tsbox.help>**

* Is the [documentation](https://ropensci.github.io/dev_guide/building.html#documentation) (installation instructions/vignettes/examples/demos) clear and sufficient?

### test `tsbox` function help files:

```{r test-help}
help(package = "tsbox")
```

#### **comments:**

> URL 'help/library/tsbox/html/00Index.html' not found.
The documentation at the link provided gives a good range of demonstrations and examples. I think it is sufficient. 

***

### test `tsbox` vignettes:

```{r test-vignettes}
vignette(package = "tsbox")
```

#### **comments:**

> no vignettes found

***

## Test functionality:

- Are there **user interface improvements** that could be made?
- Are there **performance improvements** that could be made?

```{r free-style}
library("tsbox")
```

```{r parse-functions}
exports <-ls("package:tsbox")
exports
```

<!-- experiment with package functions -->

```{r exp-chunk}
source("./tsbox-review_Chamberlin_codeexperiments.R")

```

#### **comments:**

> I'm impressed that the commands are quite simple and work well for simple timeseries. When using a timeseries data frame of one variable everything worked very well. Trying to convert a data frame of several variables seemed to be more difficult though, and it wasn't clear to me that it is possible to specify which column in the data frame I want to convert. After prompting by messages in ts_xts that there were more than one column detected, I tried converting the data using ts_long(), however it seemed to be trying to pivot some of the identifier columns which were not numeric and gave an error. Once I pivoted the dataframe using pivot_longer, I was able to plot, convert, and scale the data.

> I'm not sure I understand how the ts_plot function is supposed to work - I provided data frames with both POSIXct and character formatting for date/times and got different errors for each.

> For the character timestamps: 
`[time]: 'DateTime' [value]: 'Value' 
Error in colnamesInt(x, neworder, check_dups = FALSE) : 
  argument specifying columns specify non existing column(s): cols[3]='Value'`
  
> For the POSIXct timestamps:
`[time]: 'dateTime' [value]: 'X_00060_00000' 
Error in setnames(x, c(cid, ctime, cvalue), c("id", "time", "value")) : 
  Items of 'old' not found in column names: [X_00060_00000]. Consider skip_absent=TRUE.`
  
> When including skip_absent=TRUE:
`Error in FUN(X[[i]], ...) : ts_boxable(x) is not TRUE` 


***

## Inspect code:

- Does the package **comply with the [ROpenSci packaging guide](https://ropensci.github.io/dev_guide/building.html)**?
    * good [function & variable naming?](https://ropensci.github.io/dev_guide/building.html#function-and-argument-naming)
    * good [dependency management](https://ropensci.github.io/dev_guide/building.html#package-dependencies)?
- Are there **improvements** that could be made to the [**code style?**](https://ropensci.github.io/dev_guide/building.html#code-style)
- Is there **code duplication** in the package that should be reduced?

```{r inspect-code}
pkgreviewr::pkgreview_print_source("tsbox")
```
**\* might not be suitable for large packages with many exported functions**


<br>
<br>

#### **comments:**

> The function namings are intuitive. Dependecies seem to be well handled.


## Review test suite:

See guidance on [testing](https://ropensci.github.io/dev_guide/building.html#testing) for further details.

### test coverage

```{r pkg_coverage}
try(covr::package_coverage(pkg_dir))

```

### inspect [tests](https://github.com/christophsax/tsbox/blob/master/tests/testthat)


#### **comments:**

> Did not review.


***
